
\section{Strategy}

The development and implementation of the project is based on some
structural and visual frameworks. Each framework implements a certain amount of
features, which are required for the application.

The five most important ones are the following:
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  AngularJS
\item
  Twitter Bootstrap
\item
  d3.js
\item
  hibernate.spatial
\item
  Maven
\end{enumerate}

\subsection{\href{http://angularjs.org/}{\textbf{AngularJS}}}\label{angularjs}

AngularJS is an open source JavaScript MVC (model-view-controller)
Framework maintained by Google for writing dynamic web applications. It
offers the possibility to extend the standard HTML language, two-way
data binding and dependency injection. For a more detailed introduction
see the \href{http://docs.angularjs.org/guide/introduction}{AngularJS}
documentation.

\subsection{\href{http://getbootstrap.com/components/}{\textbf{Twitter
Bootstrap}}}\label{twitter-bootstrap}

Twitter Bootstrap is an open source collection of tools for web
development. It comprises of a number of HTML and CSS based design
templates for buttons, forms, navigation etc and a number of JavaScript
dependant dynamic extensions. See the
\href{http://getbootstrap.com/}{website} for details.

\subsection{\href{http://d3js.org/}{\textbf{d3.js}}}\label{d3.js}

d3.js is a JavaScript library using HTML, CSS and SVG to visualize data.
It uses pre-built JavaScript functions to select elements, create SVG
objects, style them, or add transitions, dynamic effects or tooltips to
them. The objects can also be styled using CSS. Datasets can be bound to
SVG objects using simple D3 functions to generate graphics.

\subsection{\href{http://www.hibernatespatial.org/}{\textbf{Hibernate
Spatial}}}\label{hibernate-spatial}

Hibernate Spatial is an extension to Hibernate to handle geographic
data. It uses the Java Topology Suite as its geometry model. JTS is an
implementation of the OpenGIS Simple Features Implementation
Specification for SQLv. 1.1 (SFS). This specification is implemented in
most RDBMS with spatial data support. It is also a direct precursor to a
precursor to SQL/MM Part 3: Spatial (ISO/IEC 13249-3).

\subsection{\href{http://maven.apache.org/}{\textbf{Apache
Maven}}}\label{apache-maven}

Apache Maven is a software project management tool. Based on the concept
of a project object model (POM), Maven can manage a project's build,
reporting and documentation from a central source repository. In our
project is used for dependency and build management.